HO unification from object language to meta language

### 2024-03-20 paper/appendix.tex
code refactor
refactor maybe-eta-of

@@

\section{The compiler}
% \begin{figure*}
% \caption{Implementation of the compiler}
% \label{code:ue-pred}
% \Description[code:ue-pred]{code:ue-pred}
% \end{figure*}

>>>>

\section{The memory}

\begin{elpicode}
  kind address type.
  type addr nat -> address.

  typeabbrev (mem A) (list (option A)).

  type get nat -> mem A -> A -> o.
  get z (some Y :: _) Y.
  get (s N) (_ :: L) X :- get N L X.

  type alloc-aux nat -> mem A -> mem A -> o.
  alloc-aux z [] [none] :- !.
  alloc-aux z L L.
  alloc-aux (s N) [] [none | M] :- alloc-aux N [] M.
  alloc-aux (s N) [X | L] [X | M] :- alloc-aux N L M.

  type alloc address -> mem A -> mem A -> o.
  alloc (addr A as Ad) Mem1 Mem2 :- unset? Ad Mem1, 
    alloc-aux A Mem1 Mem2.

  type new-aux mem A -> nat -> mem A -> o.
  new-aux [] z [none].
  new-aux [A | As] (s N) [A | Bs] :- new-aux As N Bs.

  type new mem A -> address -> mem A -> o.
  new Mem1 (addr Ad) Mem2 :- new-aux Mem1 Ad Mem2.

  type set? address -> mem A -> A -> o.
  set? (addr A) Mem Val :- get A Mem Val.

  type unset? address -> mem A -> o.
  unset? Addr Mem :- not (set? Addr Mem _).

  type assign-aux nat -> mem A -> A -> mem A -> o.
  assign-aux z (none :: L) Y (some Y :: L).
  assign-aux (s N) (X :: L) Y (X :: L1) :- assign-aux N L Y L1.

  type assign address -> mem A -> A -> mem A -> o.
  assign (addr A) Mem1 Val Mem2 :- assign-aux A Mem1 Val Mem2.
\end{elpicode}

@@

\section{The compiler}

\begin{elpicode}

\end{elpicode}
% \begin{figure*}
% \caption{Implementation of the compiler}
% \label{code:ue-pred}
% \Description[code:ue-pred]{code:ue-pred}
% \end{figure*}
